Model for categorical choice scenarios (experiments 4 to 6)

### 2023-05-31 Experiment_4/model.Rmd
adding model for exp 1 to 3 and cleaning model for exp 4 to 6

---
title: "Model"
output: 
  html_document: 
    keep_md: yes
date: "2023-04-08"
---

@@

## Load packages
```{r, Message=FALSE}
library(tidyverse)
library(gghalves) # for plots
library(patchwork)
```

## Set plot theme
```{r}
#set general theme for plots
plot_theme <- theme_minimal(base_size = 12) +
  theme(# Bold, bigger title
        plot.title = element_text(face = "bold", size = rel(1.7)),
        # Plain, slightly bigger subtitle that is grey
        plot.subtitle = element_text(face = "plain", size = rel(1.3), color = "grey70"),
        # Bold legend titles
        legend.title = element_text(face = "bold"),
        # Bold axis titles
        axis.title = element_text(face = "bold"))
```

@@

@@

```{r}
# Imagine a situation with 3 choice options
options <- 3
# generate a uniform competence distribution for a population of n = 10'000
population <- 10000
data <- data.frame(competence = runif(population, min = 1/options, max = 1))

@@

# generated population
ggplot(data, aes(x = relative_competence)) +
  geom_histogram() + 
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1)) + 
  annotate("text", x = 0.9, y = 100, label = paste0("n = ", population), color = "red") +
  labs(title = "(sampled) Population of competence drawn from \n uniform population distribution", 
       y = "Count")
```
### Generate choices from competence

### Sample choice

### Iterate this process

## Function for single population

```{r}
simulate_single_population <- function(population, sample, options, 
                                       distribution = "uniform") {
  # Check if population is not divisible by sample without remainder
  if (population %% sample != 0) {
    warning("Population is not divisible by sample without remainder.")
  }

@@

  return(results)
}

@@

```{r}
# # test output (set return to data above)
# test <- simulate_single_population(population = 600, sample = 6, options = 3) %>% arrange(sample_id)
# levels(as.factor(test$constellation))
# 
# test %>% filter(constellation == "intermediate majority")
```

## Function for various populations
```{r}
simulate_various_populations <- function(iterations,...) {

@@

## Function for varying choice options and sample size function

@@

```{r}
# set name
file_name <- "model.csv" # change for new analyses / or delete file to re-use same name

@@

      write_csv(data, paste0("data/", file_name))
    }
  }
}

# # You can test the function using the commented code below
# # (un-comment by highlighting, then command+shit+c)
# test <- do.call(power_by_sample_size,
#                 c(parameters,
#                   list(file_name = file_name, sample_sizes = c(5, 10),
#                        iterations = 100)
#                   )
#                 )
```

## Plot functions

### a) Plot various populations

First, we want a function that plots results obtained by the `simulate_various_populations` function. 
```{r}
plot_results <- function(data, outcome = "everything") {

@@

  # plot for competence
  plot_competence <- ggplot(d,
                            aes(x = constellation, y = average_competence, fill = constellation)) +
    geom_half_violin(position = position_nudge(x = -.2),
                     adjust=2, alpha = .8,
                     side = "l") +
    stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
    stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
    # Add nice labels
    labs(x = "Convergence", y = "Competence") +
    scale_fill_viridis_d(option = "plasma", begin = 0.1) +
    guides(fill = FALSE) +
    plot_theme + 
    theme(axis.text.x = element_text(angle = 20, hjust = 1)) +
    ylim(c(0, 1))

@@

### b) Plot varying sample options

@@

```{r}
plot_results_vary <- function(data, variable = options) {

@@

  # plot for accuracy
  plot_accuracy <- ggplot(d,
                          aes(x = as.factor({{variable}}), y = average_accuracy, fill = constellation)) +
    geom_half_violin(position = position_nudge(x = -.2),
                     adjust=2, alpha = .8,
                     side = "l") +
    stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
    stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
    # Add nice labels
    labs(x = x_label, y = "Accuracy") +
    scale_fill_viridis_d(option = "plasma", begin = 0.1, 
                         limits = rev(levels(d$constellation)),
                         direction = -1
    ) +
    plot_theme

  # plot for competence
  plot_competence <- ggplot(d,
                            aes(x = as.factor({{variable}}), y = average_relative_competence, fill = constellation)) +
    geom_half_violin(position = position_nudge(x = -.2),
                     adjust=2, alpha = .8,
                     side = "l") +
    stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
    stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
    # Add nice labels
    labs(x = x_label, y = "Relative competence", fill = NULL) + 
    scale_fill_viridis_d(option = "plasma", begin = 0.1, 
                         limits = rev(levels(d$constellation)),
                         direction = -1
    ) +
    plot_theme

@@

## Simulate

```{r, message=FALSE}
n <- c(3, 10, 50, 100, 200)

vary_sample_options(n = n, vary = "options", iterations = 100, population = 999, sample = 3, file_name = "model_3_options.csv")
vary_sample_options(n = n, vary = "sample", iterations = 100, population = 999, options = 3, file_name = "model_3_samples.csv")

data_3_options <- read_csv("data/model_3_options.csv")
data_3_sample <- read_csv("data/model_3_samples.csv")

plot_results_vary(data_3_options)
plot_results_vary(data_3_sample, variable = sample)

@@

```{r}
regression_data <- data_3_options %>% 
  filter(options %in% c(3, 10)) %>% 
  group_by(iteration, constellation, options) %>% 
  summarise(across(c(average_accuracy, average_relative_competence), mean)) %>% 
  mutate(
    convergence = case_when( 
      constellation == "minority" ~ 0, 
      constellation == "dissensus" ~ 1,
      constellation == "majority" ~ 2,
      constellation == "consensus" ~ 3), 
    options = as.factor(options)
  )

accuracy <- lm(average_accuracy ~ convergence + options, 
               data = regression_data) #%>% broom.mixed::tidy()
competence <- lm(average_relative_competence ~ convergence + options, data = regression_data) %>% broom.mixed::tidy()

summary(accuracy)
```

```{r}
data_3_options %>% group_by(sample, constellation) %>% summarise(across(c(average_accuracy, average_relative_competence), mean))

# make descriptive data
data_3_sample %>% 
  group_by(sample, constellation) %>% 
  summarise(count = sum(count)) %>% 
  mutate(rel_freq = round(count / sum(count), digits = 2)) %>% 
  print(n = 100)
```

## Simulate

Note that in the current state, we cannot vary `sample`. The function needs modification first. The problem is that it gets complicated with more than three informants, in the case of a majority constellation. There might be equal majorities (e.g. 5 informants, three options: 2 agree on 'A', 2 on 'B', one picks 'A'), equal minorities (e.g. 3 agree on 'A', one picks 'B', another picks 'C'), and unequal majorities (e.g. 3 agree on 'A', 2 agree on 'B').

I have to think about it again.

```{r}
data_3 <- simulate_various_populations(iterations = 100, population = 999, sample = 3, options = 3)
```

```{r}
data_3 %>% group_by(constellation) %>% summarise(across(c(average_accuracy, average_competence), mean))
```

```{r}
plot_results(data_3)
model_accuracy <- plot_results(data_3, outcome = "accuracy")
model_competence <- plot_results(data_3, outcome = "competence")
```

```{r}
# # example to check essential parts of the function
# my_strings <- c("apple", "banana", "apple", "banana", "apple")
# 
# bla <- tibble(id = rep(1:5, each = 5), 
#        string = sample(c("apple", "banana"), 25, replace = TRUE, 
#                        prob = c(0.8, 0.2)))
# 
# bla %>% group_by(id, string) %>% 
#   mutate(n_answer_in_group = n()) %>% 
#   group_by(id) %>% 
#   mutate(
#     unique_answers = n_distinct(string),
#     minority = ifelse(id == 4, 
#                       n_answer_in_group == min(n_answer_in_group), 
#                       NA
#                       )
#     ) %>% arrange(id) 
```

## Combine with plots from paper

### Make plots from data
```{r, message = FALSE}
# read data
d <- read_csv("./data/cleaned.csv")

@@

```{r}
# plot for accuracy
plot_accuracy <- ggplot(d,
       aes(x = convergence_categorical, y = accuracy, fill = convergence_categorical)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .8,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Accuracy") +
  scale_fill_viridis_d(option = "plasma", begin = 0.1) +
  guides(fill = FALSE) +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

```{r}
# plot for competence
plot_competence <- ggplot(d,
       aes(x = convergence_categorical, y = competence, fill = convergence_categorical)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .8,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Competence") +
  scale_fill_viridis_d(option = "plasma", begin = 0.1) +
  guides(fill = FALSE) +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

### combine plots from data and from model

```{r}
# accuracy
plot_accuracy <- plot_accuracy + ggtitle("Participants")
model_accuracy<- model_accuracy + ggtitle("Model")

plot_accuracy + model_accuracy
```

```{r}
# competence
plot_competence <- plot_competence + ggtitle("Participants")
model_competence<- model_competence + ggtitle("Model")

plot_competence + model_competence
```

## Have only one population.

```{r}
simulate_single_population <- function(population, sample, options) {

  # randomly draw competence levels
  data <- tibble(id = 1:population,
                 competence = runif(population, min = 1/options, max = 1))

  # randomly draw individual answers based on competence levels 
  data$answer <- data$competence %>% 
    purrr::map_chr(function(x){

  # randomly assign samples in population
  data <- data %>% mutate(sample_id = rep(1:(population/sample), sample))

  # identify constellations 
  data <- data %>% 
    # identify how often a one type of answer occurs in one group
    group_by(sample_id, answer) %>% 
  mutate(n_answer_in_sample = n()) %>% 
    # assign constellations
  group_by(sample_id) %>% 
    mutate(unique_answers = n_distinct(answer),
           # Build a first version of constellation variable
           constellation = case_when(unique_answers == sample ~ "dissensus", 
                                     unique_answers == 1 ~ "consensus",
                                     unique_answers <  sample ~ "majority"
           ),
           # identify minority answers in majority constellations
           minority = ifelse(constellation == "majority", 
                             # report whether occurences of answer within a group
                             # are the minority within that group
                             n_answer_in_sample == min(n_answer_in_sample),
                             # for all other constellations, simply code NA,
                             NA
           ), 
           # identify majority answers in majority constellations
           majority = ifelse(constellation == "majority", 
                             # report whether occurrences of answer within a group
                             # are the minority within that group
                             n_answer_in_sample == max(n_answer_in_sample),
                             # for all other constellations, simply code NA,
                             NA
           ), 
           # modify the constellation variable to distinguish between minority, 
           # intermediate majority, majority and dissensus that is composed of 
           # multiple answers (e.g. 3 options, sample of 6, two per option)
           constellation = case_when(
             is.na(minority) | is.na(majority) ~ constellation, 
             minority == TRUE & majority == TRUE ~ "dissensus",
             minority == TRUE ~ "minority", 
             majority == TRUE ~ "majority", 
             .default = "intermediate majority")
           ) %>% ungroup()

  # compute the summary statistics by constellation
  results <- data %>% 
    group_by(sample_id, constellation) %>% 
    summarize(average_competence = mean(competence), 
              average_accuracy = mean(accurate)) %>% 
    # store simulation information
    mutate(population = population, 
           sample = sample, 
           options = options) %>%

  return(results)
}

```{r}
plot_results <- function(data) {

  d <- data
  # make constellation a factor with the right levels
  d$constellation <- fct_relevel(d$constellation, "minority", "dissensus", "intermediate majority", "majority", "consensus")

  # make count data
  counts <- d %>% group_by(constellation) %>% count()

  # plot for accuracy
  plot_accuracy <- ggplot(d,
                          aes(x = constellation, y = average_accuracy, fill = constellation)) +
    geom_half_violin(position = position_nudge(x = -.2),
                     adjust=0.1, alpha = .8,
                     side = "l") +
    stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
    stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
    # Add nice labels
    labs(x = "Convergence", y = "Accuracy") +
    scale_fill_viridis_d(option = "plasma", begin = 0.1) +
    scale_color_viridis_d(option = "plasma", begin = 0.7) +
    guides(fill = FALSE, color = FALSE) +
    plot_theme + 
    theme(axis.text.x = element_text(angle = 20, hjust = 1)) +
    geom_text(data = counts, aes(x = constellation, y = 1.05, 
                                 label =  paste0("n =", n)
                                 )
              )

  # plot for competence
  plot_competence <- ggplot(d,
                            aes(x = constellation, y = average_competence, fill = constellation)) +
    geom_half_violin(position = position_nudge(x = -.2),
                     adjust=1, alpha = .8,
                     side = "l") +
    stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
    stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
    # Add nice labels
    labs(x = "Convergence", y = "Competence") +
    scale_fill_viridis_d(option = "plasma", begin = 0.1) +
    scale_color_viridis_d(option = "plasma", begin = 0.7) +
    guides(fill = FALSE) +
    plot_theme + 
    theme(axis.text.x = element_text(angle = 20, hjust = 1))

  (plot_accuracy | plot_competence)
}
```

>>>>

---
title: "Model for categorical choice scenarios (experiments 4 to 6)"
output: 
  html_document: 
    keep_md: yes
date: "2023-04-08"
---

@@

```{r, message=FALSE, echo=FALSE}
# Load packages
library(tidyverse)
library(gghalves) # for plots
library(patchwork)
library(lme4) # for linear mixed models
library(lmerTest) # p-values for mixed models
library(broom) # for tidy outputs of regressions
library(broom.mixed) # for tidy outputs of linear mixed models
```

```{r, echo=FALSE}
#set general theme for plots
plot_theme <- theme_minimal(base_size = 12) +
  theme(# Bold, bigger title
        plot.title = element_text(face = "bold", size = rel(1.7)),
        # Plain, slightly bigger subtitle that is grey
        plot.subtitle = element_text(face = "plain", size = rel(1.3), color = "grey70"),
        # Bold legend titles
        legend.title = element_text(face = "bold"),
        # Bold axis titles
        axis.title = element_text(face = "bold"))
```

```{r}
# ensure this script returns the same results on each run
set.seed(7643)
```

@@

```{r}
# Imagine a situation with 3 choice options
options <- 3
# and a population of n = 999
population <- 999
# and we observe samples of 3
sample <- 3
```

@@

```{r}
# 1: Distribution of competence
data <- data.frame(competence = runif(population, min = 1/options, max = 1))

@@

# generated population
ggplot(data, aes(x = relative_competence)) +
  geom_histogram() + 
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1)) + 
  annotate("text", x = 0.9, y = 100, label = paste0("n = ", population), color = "red") +
  labs(title = "(sampled) Population of competence drawn from \n uniform population distribution", 
       y = "Count")
```

### Generate a choice for each individual based on their competence.

```{r}
# 2: Draw individual answers based on competence levels 
data$answer <- data$competence %>% 
  purrr::map_chr(function(x){

    answer = sample(answer_options, 
                    size = 1, 
                    prob = probabilities
                    )
  }
  )

data <- data %>% 
  mutate(correct = ifelse(str_detect(answer, "correct"), 
                                        TRUE, FALSE))

answers <- ggplot(data, aes(x = answer, fill = correct)) +
  geom_bar() +
  guides(fill = "none") +
  plot_theme

competence_by_answers <- ggplot(data, 
       aes(x = answer, y = relative_competence, fill = correct)) +
geom_half_violin(position = position_nudge(x = -.2),
                     adjust=2, alpha = .8,
                     side = "r") +
  coord_flip() +
  guides(fill = "none") +
  plot_theme

answers + competence_by_answers
```

### Draw samples, assign categories & compare average outcomes

### Randomly draw samples from the population

```{r}
# 3: randomly assign samples in population
data <- data %>% mutate(sample_id = rep(1:(population/sample), sample))
```

### Categorize constellations.

```{r}
# 4: identify constellations 
data <- data %>% 
  # identify how often a one type of answer occurs in one group
  group_by(sample_id, answer) %>% 
  mutate(n_answer_in_sample = n()) %>% 
  # assign constellations
  group_by(sample_id) %>% 
  mutate(unique_answers = n_distinct(answer),
         # Build a first version of constellation variable
         constellation = case_when(unique_answers == sample ~ "dissensus", 
                                   unique_answers == 1 ~ "consensus",
                                   unique_answers <  sample ~ "majority"
         ),
         # identify minority answers in majority constellations
         minority = ifelse(constellation == "majority", 
                           # report whether occurences of answer within a group
                           # are the minority within that group
                           n_answer_in_sample == min(n_answer_in_sample),
                           # for all other constellations, simply code NA,
                           NA
         ), 
         # identify majority answers in majority constellations
         majority = ifelse(constellation == "majority", 
                           # report whether occurrences of answer within a group
                           # are the majority within that group
                           n_answer_in_sample == max(n_answer_in_sample),
                           # for all other constellations, simply code NA,
                           NA
         ), 
         # modify the constellation variable to distinguish between minority, 
         # intermediate majority, majority and dissensus that is composed of 
         # multiple answers (e.g. 3 options, sample of 6, two per option)
         constellation = case_when(
           is.na(minority) | is.na(majority) ~ constellation, 
           minority == TRUE & majority == TRUE ~ "dissensus",
           minority == TRUE ~ "minority", 
           majority == TRUE ~ "majority", 
           .default = "intermediate majority")
  ) %>% ungroup()
```

### Compute average accuracy/competence by constellation.

```{r}
# 5: calculate accuracy and competence levels per constellation

# compute the summary statistics by constellation
results <- data %>% 
  group_by(constellation) %>% 
  summarize(average_competence = mean(competence), 
            average_relative_competence = mean(relative_competence),
            average_accuracy = mean(accurate)) %>% 
  # store simulation information
  mutate(population = population, 
         sample = sample, 
         options = options)
```

```{r}
ggplot(results,
       aes(x = constellation, y = average_accuracy, fill = constellation)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .8,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Accuracy") +
  scale_fill_viridis_d(option = "plasma", begin = 0.1) +
  guides(fill = "none") +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1)) +
  ylim(c(0, 1))
```

## Functions

### Data generating functions

#### Single population

```{r, echo=FALSE}
simulate_single_population <- function(population, sample, options, 
                                       distribution = "uniform", 
                                       return = "summarized") {
  # Check if population is not divisible by sample without remainder
  if (population %% sample != 0) {
    warning("Population is not divisible by sample without remainder.")
  }

@@

  if(return == "summarized") {
    return(results)
  } else {
    return(data)
  }
}

@@

```{r, echo=FALSE}
# # test output (set return to data above)
# test <- simulate_single_population(population = 600, sample = 6, options = 3, 
#                                    return = "raw data") %>% arrange(sample_id)
# levels(as.factor(test$constellation))
# 
# test %>% filter(constellation == "intermediate majority")
```

#### Various populations

```{r, echo=FALSE}
simulate_various_populations <- function(iterations,...) {

@@

#### Vary choice options and sample size

@@

```{r, echo=FALSE}
# set name
file_name <- "model.csv" # change for new analyses / or delete file to re-use same name

@@

      write_csv(data, paste0("data/", file_name))
    }
  }
}
```

### Plot functions

#### a) Plot various populations

First, we want a function that plots results obtained by the `simulate_various_populations` function. 
```{r, echo=FALSE}
plot_results <- function(data, outcome = "everything") {

@@

  # plot for competence
  plot_competence <- ggplot(d,
                            aes(x = constellation, y =  average_relative_competence, fill = constellation)) +
    geom_half_violin(position = position_nudge(x = -.2),
                     adjust=2, alpha = .8,
                     side = "l") +
    stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
    stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
    # Add nice labels
    labs(x = "Convergence", y = "Competence") +
    scale_fill_viridis_d(option = "plasma", begin = 0.1) +
    guides(fill = FALSE) +
    plot_theme + 
    theme(axis.text.x = element_text(angle = 20, hjust = 1)) +
    ylim(c(0, 1))

@@

#### b) Plot varying sample & options

@@

```{r, echo=FALSE}
plot_results_vary <- function(data, variable = options) {

@@

  # plot for accuracy
  plot_accuracy <- ggplot(d,
                          aes(x = as.factor({{variable}}), y = average_accuracy, fill = constellation)) +
    geom_half_violin(position = position_nudge(x = -.2),
                     adjust=2, alpha = .5,
                     side = "l") +
    stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
    stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
    # Add nice labels
    labs(x = x_label, y = "Accuracy") +
    scale_fill_viridis_d(option = "plasma", begin = 0.1, 
                         limits = rev(levels(d$constellation)),
                         direction = -1
    ) +
    plot_theme

  # plot for competence
  plot_competence <- ggplot(d,
                            aes(x = as.factor({{variable}}), y = average_relative_competence, fill = constellation)) +
    geom_half_violin(position = position_nudge(x = -.2),
                     adjust=2, alpha = .5,
                     side = "l") +
    stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
    stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
    # Add nice labels
    labs(x = x_label, y = "Relative competence", fill = NULL) + 
    scale_fill_viridis_d(option = "plasma", begin = 0.1, 
                         limits = rev(levels(d$constellation)),
                         direction = -1
    ) +
    plot_theme

@@

## Simulation

### Fixed sample and choice options

#### Generate data

```{r}
file_name <- "model_3_sample_3_options.csv" # change for new analyses / or delete file to re-use same name

if (!file.exists(paste0("data/", file_name))) {

  # generate data
  data <- simulate_various_populations(iterations = 1000, population = 999, sample = 3, options = 3)

# read simulated data from .csv files
data_3 <- read_csv(paste0("data/", file_name))

# descriptive
data_3 %>% group_by(constellation) %>% summarise(across(c(average_accuracy, average_competence), mean))
```

#### Plot

```{r}
plot_results(data_3)
plot_accuracy_model <- plot_results(data_3, outcome = "accuracy")
plot_competence_model <- plot_results(data_3, outcome = "competence")
```

#### Analyze

```{r, echo=FALSE}
# possible analysis
regression_data <- data_3 %>%
  mutate(
    # make numeric version of convergence
    convergence = case_when( 
      constellation == "minority" ~ 0, 
      constellation == "dissensus" ~ 1,
      constellation == "majority" ~ 2,
      constellation == "consensus" ~ 3), 
    # scale accuracy to reach from 0 to 100 (instead from 0 to 1)
    average_accuracy = average_accuracy*100,
    # scale competence to reach from 1 to 7 (instead of 0 to 1)
    average_relative_competence = 6*average_relative_competence + 1 
  )

accuracy_model <- lm(average_accuracy ~ convergence, 
                     data = regression_data)
competence_model <- lm(average_relative_competence ~ convergence, 
                       data = regression_data)

@@

### Varying sample and choice options

### Generate data

```{r, message=FALSE}
n <- c(3, 5, 10, 20, 50, 100)

# run simulation and store results in .csv files
vary_sample_options(n = n, vary = "options", iterations = 1000, population = 999, sample = 3, file_name = "model_vary_options_3_sample.csv")
vary_sample_options(n = n, vary = "sample", iterations = 1000, population = 999, options = 3, file_name = "model_vary_sample_3_options.csv")

# read simulated data from .csv files
data_3_options <- read_csv("data/model_vary_options_3_sample.csv")
data_3_sample <- read_csv("data/model_vary_sample_3_options.csv")

### Plot

```{r, echo=FALSE}
# plot results
plot_results_vary(data_3_options)
plot_results_vary(data_3_sample, variable = sample)
```

### Analyze

```{r, echo=FALSE}
# possible analysis
regression_data <- data_3_options %>% 
  filter(options %in% c(3, 10)) %>% 
  group_by(iteration, constellation, options) %>% 
  summarise(across(c(average_accuracy, average_relative_competence), mean)) %>% 
  mutate(
    convergence = case_when( 
      constellation == "minority" ~ 0, 
      constellation == "dissensus" ~ 1,
      constellation == "majority" ~ 2,
      constellation == "consensus" ~ 3), 
    options = as.factor(options), 
    # scale accuracy to reach from 0 to 100 (instead from 0 to 1)
    average_accuracy = average_accuracy*100,
    # scale competence to reach from 1 to 7 (instead of 0 to 1)
    average_relative_competence = 6*average_relative_competence + 1
  )

accuracy <- lm(average_accuracy ~ convergence + options + convergence*options, 
               data = regression_data) 
competence <- lm(average_relative_competence ~ convergence + options, data = regression_data)

summary(competence)
```

## Compare model vs. participants

```{r, message=FALSE}
# read data from experiments
d <- read_csv("./data/cleaned.csv")

@@

### Table

```{r, echo=FALSE}
# Calculate models for participants

# model for accuracy
# random intercept and slope by participants
accuracy_participants <- lmer(accuracy ~ convergence + (1 + convergence | id), 
                                 data = d)
# model for competence
# random intercept and slope by participants
competence_participants <- lmer(competence ~ convergence + 
                           (1 + convergence | id), data = d)
```

```{r, echo=FALSE}
# main result table
modelsummary::modelsummary(list("Accuracy" = accuracy_participants, 
                                "Competence" = competence_participants,
                                "Accuracy" = accuracy_model, 
                                "Competence" = competence_model
                                ),
                           title = 'Participants vs. Model', 
                           stars = TRUE) %>%
  kableExtra::add_header_above(c(" " = 1, "Participants" = 2, "Model" = 2))
```

### Plots

#### Participant data

```{r, echo=FALSE}
# plot for accuracy
plot_accuracy <- ggplot(d,
       aes(x = convergence_categorical, y = accuracy, fill = convergence_categorical)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .8,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Accuracy") +
  scale_fill_viridis_d(option = "plasma", begin = 0.1) +
  guides(fill = FALSE) +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

```{r, echo=FALSE}
# plot for competence
plot_competence <- ggplot(d,
       aes(x = convergence_categorical, y = competence, fill = convergence_categorical)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .8,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Competence") +
  scale_fill_viridis_d(option = "plasma", begin = 0.1) +
  guides(fill = FALSE) +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

#### Combine participant and model

```{r, echo=FALSE}
# accuracy
plot_accuracy <- plot_accuracy + ggtitle("Participants")
plot_accuracy_model <- plot_accuracy_model + ggtitle("Model")

plot_accuracy + plot_accuracy_model
```

```{r, echo=FALSE}
# competence
plot_competence <- plot_competence + ggtitle("Participants")
plot_competence_model <- plot_competence_model + ggtitle("Model")

plot_competence + plot_competence_model
```
